### 2016-05-16 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Home edits

pdf('Figures/Figure 4.pdf',
    width = 4,
    height = 9,
    paper = 'a4')
multiplot(Fig4A,Fig4B,Fig4C,layout=matrix(c(1,2,3),nrow=3,byrow=T))
dev.off()

>>>>

temp <- Loss
temp$LossL <- ifelse(temp$Loss>0,'Lengthening','Shortening')

Fig4D <- ggplot(temp,aes(col=LossL,fill = LossL,y = Loss,x = TimeDiff))+
    geom_point()+
  stat_smooth(method = 'lm')+
  theme_classic()+
  xlab ('Follow up time (years)')+
  ylab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c(0.8,0.9),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
    geom_abline(slope = 0,intercept = 0,lty = 2)+
  annotate('text',x = 0,y = 1,label = 'D')

pdf('Figures/Figure 4.pdf',
    width = 8,
    height = 7,
    paper = 'a4')
multiplot(Fig4A,Fig4B,Fig4C,Fig4D,layout=matrix(c(1,2,3,4),nrow=2,byrow=T))
dev.off()
